Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-23 paper/ijcai/paper.tex
pass on statistical tests

        \lang{}            & 100 & 96.9\\
        \cmath{}           & 89.4 & 95.2\\
        %\closure{}          &  & \\
		\chart{}			& 76.9 & 84.6 \\
        \jtime{}            & 81.5 & 85.2\\
        \mockito{}          & 71.1 & 78.9\\

@@

\begin{table*}[t!]
	\small
	% \setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|cc|cc|c}
		\toprule
		 Project        &   \sfl{}$^{5}$   & \combpar{5}
		 				&   \sfl{}$^{10}$   & \combpar{10}& \# Faults      \\
		\midrule
		 \lang{}         &   84.6   & 100 & 84.6 & 96.9 & 65      \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 & 104  \\   
		\chart{}           & 84.6 & 76.9 & 92.3 & 84.6 & 26  \\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2 & 27  \\   
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9 & 38  \\   \midrule
		Total         & 79.6 & 87.3 & 83.5 & 91.2 & 260  \\  
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\end{table*}

@@

The first experiment we ran to assess impact consisted of measuring
the \emph{difference of diagnosis cost}. This metric has been
previously used in other studies~\Fix{cite cite}. More specifically,
we computed $\Delta{}C = C(\textrm{SFL$^{k}$}) -
C(\textrm{\combpar{k}})$, where $C$ denotes the diagnosis cost and is
obtained by computing the mean position in the ranking of all buggy
statements. $\Delta C >0$ means that the position of the faulty
statement has decreased with \combpar{k}, \ie{}, the combination had a
positive impact. $\Delta C <0$ means that \combpar{k} performs worse
compared to its baseline. That could happen if dynamic slicing misses
the faulty statement---the statements not included in the slice will
have their suspiciousness scores reduced and ranks potentially
reduced. $\Delta C=0$ means that the faulty statement remained in the
same position.  It is worth noting that we assume a perfect bug
understanding, i.e., if the developer sees the bug in the ranking, he
is able to precisely determine if it is the faulty one.

\Mar{I see there are different results/metrics/tables. We need to
  organize this better, with sub-questions or stating different
  other experiments to answer the main question.}

@@

Figure \ref{fig:diagnosis} reports the cost of diagnosis of using \combpar{5} and \combpar{10} instead of \sfl{}$^{5}$ and \sfl{}$^{10}$,
respectively. For $k=5$, we observe that in $30$ ($11.5\%$) of the faults
the position of faulty statements decreases
in the ranking, $97$($37.3\%$) of the faults the position of faulty statements increases in the rankinh whereas $133$ ($51.2\%$) of the faults the position of faulty stamenets remains the same. For $k=10$, we observe an increasing of $20$ cases where the position of faulty statements increases in the ranking $117$ ($45.0\%$).
The number of cases whose faulty statements position remained the same are $110$ ($42.3\%$) and that suffered a decrease in the ranking is $33$ ($12.7\%$).

@@

Although this dataset has more than $50\%$ of fault of omissions,
our simple slicing approach was capable of improving the ranking of $95$ faults for
$k=5$ and $115$ faults for $k=10$. Table \ref{table:st} presents the statistics
to determine if the observed results are statistically significant. Shapiro-Wilk
tests the null hypothesis that results are drawn from a normal distribution. The
test is perfomed for all techniques and its variants. With $99\%$ of confidence,
the results tell us that the distributions are not normal. Given that $C$ is not
normally distributed, we use the non-parametrical statistical hypothesis test
Friedman. The null-hypothesis is that the ranking results of all techniques and
variants are the same. With $99\%$ of confidence, the results show that the
distributions are distinct. To understand which techniques perform differently 
- i.e., \textit{Does \combpar{10} perform differently than \sfl{}$^{10}$} -
we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all pairs of techniques. Each square represents the significance between the correspondent techniques, i.e., if it is significant it means that the techniques perform differently. With $95\%$ of confidence, it is possible to confirm that the performance of all techniques is different expect when comparing \combpar{5} with \combpar{10}.

It is worth noting that Automated
Program Repair techniques may directly benefit from this study to improve their
results.

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
		\caption{Cost of diagnosis of using \combpar{5} and \combpar{10} instead of \sfl{}$^{5}$ and \sfl{}$^{10}$, respectively}
		\label{fig:diagnosis}
\end{figure}

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
Mean & \textbf{590.7} (584.3)   &  \textbf{512.7} (516.4)  & \textbf{573.4} (679.7)  & \textbf{506.6} (614.0)   \\ \midrule
Median & \textbf{46.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1257.0} (1223.1)  &  \textbf{1171.5} (1148.1) & \textbf{1239.1} (1352.4) &  \textbf{1167.0} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 162.61 \\ p-value = 5.00 x $10^{-35}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}

>>>>

        \lang{}            & 100.0 & 96.9\\
        \cmath{}           & 89.4 & 95.2\\
        %\closure{}          &  & \\
		\chart{}			& 76.9 & 84.6 \\
        \jtime{}            & 81.5 & 85.2\\
        \mockito{}          & 71.1 & 78.9\\

@@

\begin{table}[h!]
	\small
	\setlength{\tabcolsep}{3pt}
	\centering
	  \begin{tabular}{l|rr|rr}
		 \toprule
       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
		\midrule
		 \lang{}         &   84.6   & 100.0 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\   
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\   
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 87.3 & 83.5 & 91.2\\  
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty-statements is in the \sfl{}$^{k}$ and \combpar{k} report}
  \label{table:fsws}
\end{table}

@@

The first experiment we ran to assess impact consists of measuring the
\emph{difference of diagnosis cost}. This metric has been previously
used in other studies~\Fix{cite cite}. More specifically, we computed
$\Delta{}C = C(\textrm{SFL$^{k}$}) - C(\textrm{\combpar{k}})$, where
$C$ denotes the diagnosis cost and is obtained by computing the mean
position in the ranking of all buggy statements. $\Delta C >0$ means
that the position of the faulty statement has decreased with
\combpar{k}, \ie{}, the combination had a positive impact. $\Delta C
<0$ means that \combpar{k} performs worse compared to its
baseline. That could happen if dynamic slicing misses the faulty
statement---the statements not included in the slice will have their
suspiciousness scores reduced and ranks potentially reduced. $\Delta
C=0$ means that the faulty statement remained in the same position.
It is worth noting that we assume a perfect bug understanding, i.e.,
if the developer sees the bug in the ranking, he is able to precisely
determine if it is the faulty one.

Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
relative to \sfl{}$^{k}$ using histograms over $\Delta{}C$ for
different values of $k$. Note that (1) the number of cases where
\sfl{}$^{k}$ outperforms \combpar{k} is very small compared and (2)
the number of cases \combpar{k} outperforms \sfl{}$^{k}$ is
significant and, as we increase the value of $k$, it increases (from
97 to 117 faults).

%% For $k=5$, we observe that in $30$ ($11.5\%$) of the faults the
%% position of faulty statements decreases in the ranking, $97$($37.3\%$)
%% of the faults the position of faulty statements increases in the
%% rankinh whereas $133$ ($51.2\%$) of the faults the position of faulty
%% stamenets remains the same. For $k=10$, we observe an increasing of
%% $20$ cases where the position of faulty statements increases in the
%% ranking $117$ ($45.0\%$).  The number of cases whose faulty statements
%% position remained the same are $110$ ($42.3\%$) and that suffered a
%% decrease in the ranking is $33$ ($12.7\%$).

\begin{figure}[h]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/performance.pdf}
		\caption{Histograms of $\Delta{}C$.}
		\label{fig:diagnosis}
\end{figure}

@@

@@

\begin{table}[h!]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
Mean & \textbf{590.7} (584.3)   &  \textbf{512.7} (516.4)  & \textbf{573.4} (679.7)  & \textbf{506.6} (614.0)   \\ \midrule
Median & \textbf{46.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1257.0} (1223.1)  &  \textbf{1171.5} (1148.1) & \textbf{1239.1} (1352.4) &  \textbf{1167.0} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.52 \\ $p$ = 1.75 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.50 x $10^{-25}$} & \makecell{$W$ = 0.51 \\ $p$ = 1.10 x $10^{-24}$} & \makecell{$W$ = 0.48 \\ $p$ = 2.26 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 162.61 \\ p-value = 5.00 x $10^{-35}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}

Although this dataset has more than $50\%$ of fault of omissions, our
simple slicing approach was capable of improving the ranking of $95$
faults for $k=5$ and $115$ faults for $k=10$. Table \ref{table:st}
presents the statistics to determine if the observed results are
statistically significant. Shapiro-Wilk tests the null hypothesis that
results are drawn from a normal distribution. The test is perfomed for
all techniques and its variants. With $99\%$ of confidence, the
results tell us that the distributions are not normal. Given that $C$
is not normally distributed, we use Friedman test, a non-parametric
statistical test of hypothesis. The null-hypothesis is that the
ranking results of all techniques and variants are the same. With
$99\%$ confidence, the results show that the distributions are
distinct.

To understand which techniques perform differently, \ie{} to answer
the question \textit{Does \combpar{k} perform differently than
  \sfl{}$^{k}$}, we performed a Siegel post-hoc analysis. Figure
\ref{fig:performance} reports the results of Siegel analysis for all
pairs of techniques. Each square\Mar{gray intensity?} represents the
significance\Mar{of what?} between the corresponding techniques, i.e.,
if it is significant it means that the techniques perform
differently. We can determine with $95\%$ confidence that the
performance of each pair of techniques is different.

@@
